\documentclass{article}

\usepackage{CJKutf8}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{latexsym}
\usepackage{sagetex}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{color}
\usepackage{listings}
\usepackage[unicode=true]{hyperref}

\begin{document}
\begin{CJK*}{UTF8}{gbsn}

\setlength{\parindent}{2em}
\renewcommand{\today}{\number\year 年 \number\month 月 \number\day 日}
\renewcommand{\contentsname}{目录}
\renewcommand{\refname}{参考文献}

\title{数学模型的Sage实现}
\author{hilbert}
\date{\today}
\maketitle
\newpage

\input{foreword.tex}
\newpage

\tableofcontents
\newpage
\newpage

\input{sections/mixed-integer-linear-programming.tex}
\newpage
\input{sections/non-linear-programming.tex}
\newpage
\input{sections/dynamic-programming.tex}
\newpage
\input{sections/graph-theory-and-network-analysis.tex}
\newpage
\input{sections/queuing-theory.tex}
\newpage
\input{sections/game-theory.tex}
\newpage
\input{sections/the-analytic-hierarchy-process.tex}
\newpage
\input{sections/interpolation-and-fitting.tex}
\newpage
\input{sections/statistical-description-and-analysis.tex}
\newpage
\input{sections/variance-analysis.tex}
\newpage
\input{sections/regression-analysis.tex}
\newpage
\input{sections/numerical-solution-of-differential-equation.tex}
\newpage
\input{sections/stable-state-of-differential-equation.tex}
\newpage
\input{sections/difference-equation.tex}
\newpage
\input{sections/markov-chain.tex}
\newpage
\input{sections/variational-problem.tex}
\newpage
\input{sections/artificial-neural-network.tex}
\newpage
\input{sections/goal-programming.tex}
\newpage
\input{sections/fuzzy-math.tex}
\newpage
\input{sections/tabu-search.tex}
\newpage
\input{sections/simulated-annealing.tex}
\newpage
\input{sections/genetic-algorithms.tex}
\newpage
\input{sections/time-series.tex}
\newpage
\input{sections/inventory-theory.tex}
\newpage
\input{sections/grey-system-theory.tex}
\newpage
\input{sections/multivariate-analysis.tex}
\newpage
\input{sections/partial-least-squares-regression.tex}
\newpage
\input{sections/support-vector-machine.tex}
\newpage
\input{sections/operation-plan.tex}
\newpage
\input{sections/others.tex}
\newpage

\begin{thebibliography}{99}

\bibitem{Sage-Reference} The Sage Development Team.
\newblock Sage Reference v6.1.1.
\newblock {\em The Sage Development Team, 2014, http://www.sagemath.org/doc/reference/}

\bibitem{Sage} William A. Stein et al.
\newblock Sage Mathematics Software (Version 6.1.1).
\newblock {\em The Sage Development Team, 2014, http://www.sagemath.org}

\bibitem{R} The R Development Team.
\newblock The R Environment.
\newblock {\em The R Project for Statistical Computing,2014,http://www.r-project.org}

\bibitem{math-model} 司守奎.
\newblock 数学建模算法与程序.
\newblock {\em 海军航空工程学院}

\bibitem{statistic-R} 薛毅,陈立萍.
\newblock 统计建模与R软件.
\newblock {\em 清华大学出版社}

\end{thebibliography}

\end{CJK*}
\end{document}
